### 2024-06-28 conteudo/methods/methods.tex
Add initial methods with all texts

Finishing our mitigation method, if the mitigation ended up working in a initial step, we move it foward to the 
Ethnographic method, iteracting with the Linux community to understand what are their thoughts on the mitigation. If the mitigation
ended up as not working as expected, we will categorized it in two categories, the first one is that the refactoring requires a
decision in which we, as not specialist and non-maintainers of the Linux kernel, cannot make it correctly, although
we believe a specialist would be able to refactoring it. The second categorization is that we do not know if it is in fact possible
to refactoring the duplication.

@@

>>>>

Finishing our mitigation method, if the mitigation ended up working in a initial step, we may move it foward to the 
Ethnographic method, iteracting with the Linux community to understand what are their thoughts on the mitigation. If the mitigation
ended up as not working as expected, we will categorized it in two categories, the first one is that the refactoring requires a
decision in which we, as not specialist and non-maintainers of the Linux kernel, cannot make it correctly, although
we believe a specialist would be able to refactoring it. The second categorization is that we do not know if it is in fact possible
to refactoring the duplication. With or without a sucessful mitigation, we will store our mitigations on (ADD REP AND PUT HERE) 
to research tranparency.

@@

When we make a code duplication mitigation following our approach pipeline described in \citep{subsec:pipeline}, we are apt
to initiate our ethnographic research. We resorted to a participant-observation approach as our ethnographic methodology, where we 
will act as contributors of the Linux kernel to the AMD Display driver, interacting with the maintainers of the AMD Display driver
attempting to get our mitigations added to the Linux kernel.

The Linux kernel communication is made through public mailing lists, where anyone can consult the discussions made in it.
We plan to collect data artifacts through the AMD Display diver mainling list.
The mainling list will register our iteractions with Linux community, with 
their members sharing their opinions and suggestions to the mitigation we made, corroborating to the discussion about the 
effectiveness of our proposed approach.

Given the time limit of our research, we does not expect to be able to iteract with the Linux community throughtout successfully
mitigation we made using the proposed approach, as it pass through factors we do not control, which is the time spent waiting 
for Linux community's members interact with us.
For this reason, we resorted to commit to do the participant-observation approach 
in 5 of the successfully mitigation and use them for our discussion.
